Persistence in functional topology: \\ existence of persistence diagrams and Morse inequalities

### 2021-10-14 sec/connectivity.tex
Reorder section 4

Similarly, we have the following weaker version of this property.

@@

Our main result, proven in the next subsection, is that for compact sublevel set filtrations the $\HLC$ condition implies \mbox{q-tameness} and, consequently, also the existence of a persistence diagram.

Combining \cref{t:weak hlc to hlc} and \cref{t:local connectedness implies q-tameness} we have the following consequence;
the existence of a result of this kind has been suggested by Weinberger \cite{Weinberger.2011}.

\begin{cor} \label{c:q-tameness for continuous functions}
	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is compact and weakly $\HLC$, then it is also q-tame.
\end{cor}

@@

>>>>

@@

The following result is deduced directly from \cref{t:weak hlc to hlc} and \cref{t:local connectedness implies q-tameness} below.
The existence of a result of this kind has been suggested by Weinberger \cite{Weinberger.2011}.

\begin{thm} \label{t:q-tameness for continuous functions}
	If the sublevel set filtration of a continuous function $f \colon X \to \R$ is compact and weakly $\HLC$, then it is also q-tame.
\end{thm}

@@

We consider the following stronger local connectivity condition of sublevel set filtrations.

Our main technical result, proven in the next subsection, is that for compact sublevel set filtrations the $\HLC$ condition implies \mbox{q-tameness} and, consequently, also the existence of a persistence diagram.
